Case Study/Application

### 2020-02-08 chapters/04_application.Rmd
testing bymhrs

Census block groups are split into 5 market areas based on the Transit Market Index described above, where the highest market area (Market Area 1) is expected to support high-frequency, all-day service and the lowest market area (Market Area 5) is expected to support peak commuter express service, if that.

The Transit Market Index values are geographically smoothed to create more-or-less concentric Transit Market Areas.

@@

@@

# Data Preparation

>>>>

Census block groups are split into 5 market areas based on the Transit Market Index described above, where the highest market area (Market Area 1) is expected to support high-frequency, all-day service and the lowest market area (Market Area 5) is expected to support peak commuter express service and park-and-rides, if that.

The Transit Market Index values are geographically smoothed to create more-or-less concentric Transit Market Areas. The linear regression is an intuitive way to think about transit ridership across space. The four predictors used are common-sense indicators of transit ridership: high population and employment density are characteristic of trip origins and destinations, automobile availability is reasonably assumed to be related to transit ridership, and intersection density is a proxy for the "walkability" of an area. However, the exsiting Transit Market Area model may be over-simplifying the complex question of transit ridership.

Transit ridership has been in decline in the Twin Cities, and across the country, for several years (Cite).

@@

This analysis relies on several Metro Transit provided data sets. The two primary sources are automatically reported by in-service vehicles, yielding billions of rows of observations.

**Automatic Passenger Count (APC)** data is reported every time a bus opens its doors. Two beams of light detect movement through the doors of the bus and counts the number of passengers getting on and off at each bus stop. Naturally, this data source is flawed: sometimes, vehicles fail to report data, and the sensors can be easily tricked. Someone getting off the bus pulling a suitcase behind them, for example, would likely be counted as two passengers exiting. However, APC is the most granular ridership data available, giving us the most control over our spatial aggregations of ridership. This is the primary data source used in this analysis.

**Automatic Vehicle Location (AVL)** data is similarly reported by in-service vehicles (approximately) every 8 seconds. The vehicle reports in GPS location continuously while in service. We use AVL data to adjust for missing APC data.

**Metro Transit's Schedule** as *planned*, rather than as *run*, is also used to correct missing APC data.

This analysis began by pulling all APC, AVL, and schedule data from 2015-2018. The analysis presented here focuses on 2017 data.

### Data Interpolation

In theory, we have APC data for each run bus trip in 2017. However, we know (how to cite Metro Transit knowledge?) that, for a variety of reasons, this is untrue. The automatic data reporting technology on Metro Transit's buses ///

@@
